The Emotional Coherence Controversy: Evidence from Human and Automatic Expression Recognition

### 2019-07-22 ACII_2019_paper/ACII_2019_doc.Rmd
paper doc

bibliography: mybibfile.bib
output: rticles::ieee_article
csl: http://www.zotero.org/styles/ieee
fig_caption: yes
number_sections: yes
includes:
  in_header: preamble-latex.tex
---
<!-- template: C:/Users/dupred/Desktop/Projects/dynemo_feel_express/ACII_2019_paper/conference_041818.tex -->
\begin{IEEEkeywords}
Facial expression, self-report, human observer, automatic recognition.
\end{IEEEkeywords}

@@

```{r models_img, fig.height=5, fig.cap="\\label{fig:models_img}Comparison of behaviorist and social constructivist approaches according to the expected differences in emotion recognition."}
raster::stack(here::here("./img/models.png")) %>%
  raster::plotRGB()
```

@@

```{r dynemo_img, fig.height=3, fig.cap="\\label{fig:dynemo_img}Example of a front facing recording synced with the full view of the participant and the elicitation task. This picture is taken from a pilot with projects collaborators and all gave consent for the publication of their photos and videos."}
raster::stack(here::here("./img/dynemo_img.png")) %>%
  raster::plotRGB()
```

>>>>

bibliography: mybibfile.bib
output: word_document
#output: rticles::ieee_article
csl: http://www.zotero.org/styles/ieee
fig_caption: yes
number_sections: yes
includes:
  in_header: preamble-latex.tex
---
<!-- template: C:/Users/dupred/Desktop/Projects/dynemo_feel_express/ACII_2019_paper/conference_041818.tex -->
\begin{IEEEkeywords}
Facial expression, self-report, human observer, automatic recognition.
\end{IEEEkeywords}

@@

```{r models_img, fig.height=5, fig.cap="\\label{fig:models_img}Comparison of behaviorist and social constructivist approaches according to the expected differences in emotion recognition."}
# raster::stack(here::here("./img/models.png")) %>%
#   raster::plotRGB()
knitr::include_graphics(here::here("./img/models.png"))
```

@@

```{r dynemo_img, fig.height=3, fig.cap="\\label{fig:dynemo_img}Example of a front facing recording synced with the full view of the participant and the elicitation task. This picture is taken from a pilot with projects collaborators and all gave consent for the publication of their photos and videos."}
# raster::stack(here::here("./img/dynemo_img.png")) %>%
#   raster::plotRGB()
knitr::include_graphics(here::here("./img/dynemo_img.png"))
```
